---
title: "BBets Project"
author: "Harun M"
date: "1/31/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction  

The question is how much money is won/lost on a bet that at least two people have the same b'day in a class of 35.  Instructor wagers 2:1 

Instuctor has done this 15 times,  
1.what is his expected win/loss amount,  
2. how much would the instructor have to wager to make the bet fair?  
3. how many students would have to be in the class for a 2:1 bet to be fair?   
 
 
```{r}
days = 1:365

saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:525){
    sampleClass = sample(days, 35, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == 35) bank = bank - 2
    else bank = bank + 1
  }
saveArray[k]= bank
}

```
 
histogram of bank amounts.   

```{r}
hist(saveArray)
```

Answer questions #1

```{r}
print('average amt:')
print(mean(saveArray))
```

## question 2
```{r}

saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:525){
    sampleClass = sample(days, 35, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == 35) bank = bank - 4.50
    else bank = bank + 1
  }
saveArray[k]= bank

}

print(paste('average return: ', mean(saveArray)))

```
answer to question 2:  about $4.50

## question 3   how many students to brake even at 2:1 payoff
 
```{r}

nStudents=29
 saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:525){
    sampleClass = sample(days, nStudents, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == nStudents) bank = bank - 2
    else bank = bank + 1
  }
saveArray[k]= bank
}

 print(paste('average return: ',mean(saveArray)))
```
 The number of students for break-even at 2:1 is 29
  